---
title: "Planning Unit Reconciliation Report"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
params:
  start_time: NA
  end_time: NA
  output_dir: NA
  summary_PUR: NA
  total_area: NA
  sa: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(knitr)
library(kableExtra)
library(dplyr)
library(ggplot2)
library(sf)
library(terra)
library(dplyr)
library(DT)
library(units)
```

## Summary

The total area analyzed was `r format(round(params$total_area, 2), big.mark = ",")` hectares.

## Module brief description

Planning unit reconciliation is a process to resolve overlapping permits by referring to function reference maps. Reconciliation is done by analyzing how well the permit data matches the reference data. Permit data can include things like forest management concessions, plantation permits, mining permits, and others. Reference data can be spatial planning data or area designation data.

## Results

### Reconciliation Results Map
```{r Reconciliation Result Map, echo=FALSE}

resolved_map <- params$sa
plot(resolved_map["Rec_phase2"])
```

### Reconciliation Data Summary

The table below summarizes the final reconciliation results:

```{r Reconsiliation Result Table, echo=FALSE}

table_recon <- params$summary_PUR
table_recon <- table_recon %>%
  mutate(Area = as.numeric(units::set_units(Area, "ha")),
         Area = round(Area, 0))
total_area <- sum(table_recon$Area, na.rm = TRUE)
table_recon <- table_recon %>%
  mutate(Percentage = round(Area / total_area * 100, 2))

# Create a pie chart
pie_chart <- ggplot(table_recon, aes(x = "", y = Area, fill = Rec_phase2)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y", start = 0) +
  theme_void() +
  labs(fill = "Reconciliation Class") +
  ggtitle("Distribution of Reconciled Areas")

print(pie_chart)

# Create the datatable
DT::datatable(table_recon, 
              colnames = c("ID", "Final Resolved Area", "Area (Ha)", "Percentage (%)"),
              options = list(pageLength = 10, scrollX = TRUE)) %>%
  formatStyle(columns = names(table_recon), fontSize = '90%') %>%
  formatRound(columns = "Area", digits = 0) %>%
  formatRound(columns = "Percentage", digits = 2)
```
