---
title: "Trade-off Analysis Regional 1 Report"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: kable
params:
  BPD_graph: NA
  FPD_graph: NA
  LRC_graph: NA
  Linkages_table: NA
  land.requirement_table: NA
  PRS_graph : NA 
  GDP : NA 
  GDP_graph : NA 
  multiplier : NA
  OMPL_graph : NA 
  IMPL_graph : NA 
  LMPL_graph : NA 
  P.sector.selected : NA
  session_log: NA
  int_con_path : NA  
  add_val_path : NA  
  fin_dem_path : NA
  fin_dem_struc_path : NA
  add_val_struc_path : NA
  sector_path : NA
  labour_path : NA
  land_distribution_path : NA
  land_use_path : NA
  landuse_table_path : NA
  unit: NA
  location: NA
  I_O_period : NA
  output_dir: NA
---

```{r setup, include = FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(kableExtra)
library(ggplot2)
```

<details><summary>Click here for Analysis Log</summary>

```{r analysis-log, echo=FALSE}

analysis_log <- tribble(
  ~Category,                   ~Details,
  # "Analysis Start",        params$start_time,
  # "Analysis End",          params$end_time,
  "Input Data and Parameters", "",
  "Sector table",      params$sector_path,
  "Intermediate Demand table",   params$int_con_path,
  "Final Demand Component table",   params$fin_dem_struc_path,
  "Final Demand table",   params$fin_dem_path,
  "Added Value Component table",      params$add_val_struc_path,
  "Added Value table",   params$add_val_path,
  "Labour table",   params$labour_path,
  "Land Distribution table",   params$land_distribution_path,
  "Land Use map",   params$land_use_path,
  "Land Use Lookup table",   params$landuse_table_path,
  "Unit", as.character(params$unit),
  "Location", as.character(params$location),
  "IO Period", as.character(params$I_O_period),
  "Output Files", "",
  "Output Workspace",      paste0(getwd(), " | ", params$output_dir),
  "Session Summary", "",
) %>% rbind(format_session_info_table())

analysis_log %>% kbl(caption = "Analysis Log", escape = FALSE) %>%
  kable_paper("hover", full_width = F )
```
</details>

## Introduction

This report presents the results of an analysis based on the provided maps and lookup table

## Lookup Table Summary

* A brief description or summary statistics of the lookup table data can be included here.

## Analysis Results

The maps provided was carbon, emission and sequestration map.

* Calculation or analysis details based on the results can be presented here.

## Analysis of Sectoral Linkages 
### Table 1. Sectoral linkages

```{r, echo=FALSE, warning=FALSE, message=FALSE}
knitr::kable(params$Linkages_table)
```

### Direct Backward Linkages graph
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(params$BPD_graph)
```

### Direct Forward Linkages graph 
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(params$FPD_graph)
```

### Sectoral typology based on linkages analysis
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(params$PRS_graph)
```

### Primary sectors based on potential linkage
```{r, echo=FALSE, warning=FALSE, message=FALSE}
knitr::kable(params$P.sector.selected)
```

## Analysis of GDP 
### Sectoral GDP Table
```{r, echo=FALSE, warning=FALSE, message=FALSE}
knitr::kable(params$GDP)
```

### GDP graph 
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(params$GDP_graph)
```

## Analysis of multiplier 
### Sectoral Multiplier
```{r, echo=FALSE, warning=FALSE, message=FALSE}
knitr::kable(params$multiplier)
```

### Output Multiplier
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(params$OMPL_graph)
```

### Input Multiplier
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(params$IMPL_graph)
```

### Labour Multiplier
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(params$LMPL_graph)
```

### Land Requirement Table
```{r, echo=FALSE, warning=FALSE, message=FALSE}
knitr::kable(params$land.requirement_table)
```

### Land Requirement Coefficient Graph 
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(params$LRC_graph)
```

## Conclusion

* Summarize the key findings or insights from the analysis.
