---
title: "Trade-off Analysis Regional 1 Report"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: kable
params:
  BPD_graph: NA
  FPD_graph: NA
  LRC_graph: NA
  Linkages_table: NA
  land.requirement_table: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(raster)
```

## Introduction

This report presents the results of an analysis based on the provided maps and lookup table

## Lookup Table Summary


* A brief description or summary statistics of the lookup table data can be included here.


## Analysis Results

The maps provided was carbon, emission and sequestration map.

* Calculation or analysis details based on the results can be presented here.

### Opportunity Cost Table

```{r, echo=FALSE, warning=FALSE, message=FALSE}
head(params$Linkages_table, n=20)
```

### Opportunity Cost Curve
```{r, echo=FALSE, warning=FALSE, message=FALSE}
head(params$land.requirement_table, n=20)
```

### Direct Backward Linkages graph

```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(params$BPD_graph)
```

### Direct Forward Linkages graph 
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(params$FPD_graph)
```

### Land Requirement Coefficient graph 

```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(params$LRC_graph)
```

## Conclusion

* Summarize the key findings or insights from the analysis.
