---
title: "QUES-H RUSLE - Module Report"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: kable
params:
  start_time: NA
  end_time: NA
  output_dir: NA
  dem: NA
  pu: NA
  rainfall: NA
  soil: NA
  landcover: NA
  r: NA
  k: NA
  ls: NA
  c: NA
  p: NA
  a: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = normalizePath(rprojroot::find_rstudio_root_file()))
library(knitr)
library(kableExtra)
library(dplyr)
library(ggplot2)
library(sf)
library(terra)
library(raster)
```

## Summary



## Module brief description

QuES-H (Quantification of Ecosystem Services) is a hydrological assessment module that analyzes hydrological environmental services. The current version features a soil erosion risk module based on the Revised Universal Soil Loss Equation (RUSLE), with plans to expand its capabilities to include additional hydrological analyses in the future.

## Input data

### Total Annual Precipitation Map 

Represents the total rainfall for each pixel over a year (mm/year)

```{r}
#| echo: false
#| fig-keep: all
#| message: false
#| results: false
#| warning: false

plot(params$rainfall)
```

### Digital Elevation Model (DEM) Map 

Represents the terrain elevation (meters above sea level)

```{r}
#| echo: false
#| fig-keep: all
#| message: false
#| results: false
#| warning: false

plot(params$dem)
```

### Soil Properties Maps 

Represents the soil characteristic, defined by Clay content (%), Silt content (%), Sand content (%), and Soil organic content (g/kg)

```{r}
#| echo: false
#| fig-keep: all
#| message: false
#| results: false
#| warning: false

plot(params$soil)
```

### Land Cover Map 

Categorical raster with each pixel value corresponds to a land cover class

```{r}
#| echo: false
#| fig-keep: all
#| message: false
#| results: false
#| warning: false

plot(params$landcover)
```

### Planning Unit Map

A polygon shapefile of administrative or management zones.

```{r reference-map, fig.width=12, fig.height=8}
#| echo: false
#| fig-keep: all
#| message: false
#| results: false
#| warning: false

plot(params$pu)
```

## Results

### Factor of RUSLE

#### R Factor: Rainfall Erosivity

```{r}
#| echo: false
#| fig-keep: all
#| message: false
#| results: false
#| warning: false

plot(params$r)
```

#### K Factor: Soil Erodibility

```{r}
#| echo: false
#| fig-keep: all
#| message: false
#| results: false
#| warning: false

plot(params$k)
```

#### LS Factor: Length and Steepness

```{r}
#| echo: false
#| fig-keep: all
#| message: false
#| results: false
#| warning: false

plot(params$ls)
```

#### C Factor: Cover Management

```{r}
#| echo: false
#| fig-keep: all
#| message: false
#| results: false
#| warning: false

plot(params$c)
```

#### P Factor: Practice Management

```{r}
#| echo: false
#| fig-keep: all
#| message: false
#| results: false
#| warning: false

plot(params$p)
```

### Estimation of Soil Erosion

```{r}
#| echo: false
#| fig-keep: all
#| message: false
#| results: false
#| warning: false

levelplot(a, margin = FALSE, main = "Mean Annual Erosion")

hist(a, xlim = c(0, 10000), main = "Histogramm of mean annual erosion (arbitary input layers)")
```

------------------------------------------------------------------------

<font size="1"> LUMENS is free software and comes with ABSOLUTELY NO WARRANTY. Users are responsible for the results generated. Results depend on the quality of the input data ("garbage in, garbage out") and may vary or be sensitive to the parameters used. Please report any problems encountered while using LUMENS as [a GitHub issue](https://github.com/icraf-indonesia/lumens-shiny/issues). Feedback and questions are welcome [Contact Us URL]. </font size>