---
title: "Land Suitability Evaluation Module (LaSEM) Report"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
params:
  start_time: NA
  end_time: NA
  file_name_soil_climate_factors_rds: NA
  file_name_land_suit_rds: NA
  file_name_land_suit_tif: NA
  file_name_land_suit_shp: NA
  file_name_land_suit_lookup_csv: NA
  file_name_suit_factors_tif: NA
  path_lookup_raster_inputs: NA
  path_lookup_crop_suitability: NA
  path_lookup_intervention: NA
  path_output: NA
  session_log: NA
  validation_results: NA
  inspection_log: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
library(readr)
library(dplyr)
library(terra)
library(sf)
library(knitr)
library(kableExtra)
library(DT)
library(tidyterra)
library(ggplot2)
library(patchwork)
library(stringr)
library(htmltools)
library(leaflet)
library(tidyr)

# Load data
suitability_parameter <- read_csv(params$path_lookup_crop_suitability)
climate_soil_data <- read_csv(params$path_lookup_raster_inputs)
harmonised_rasters <- terra::unwrap(readRDS(params$file_name_soil_climate_factors_rds))
suitability_polygon <- readRDS(params$file_name_land_suit_rds)
intervention_lookup <- read_csv(params$path_lookup_intervention)
suit_by_factors <- terra::rast(params$file_name_suit_factors_tif)

# Color scheme for suitability classes
suit_colors <- c(
  "S1" = "#228B22",  # Forest green
  "S2" = "#90EE90",  # Light green
  "S3" = "#FFA500",  # Orange
  "N"  = "#DC143C"   # Crimson
)

suit_labels <- c(
  "S1" = "S1 - Highly Suitable",
  "S2" = "S2 - Moderately Suitable",
  "S3" = "S3 - Marginally Suitable",
  "N"  = "N - Not Suitable"
)
```

---

**Species:** `r suitability_parameter[["name_sp"]][1]`

**Common name:** `r suitability_parameter[["name_common"]][1]`

**Analysis period:** `r params$start_time` to `r params$end_time`

---

<details open><summary><strong>Analysis Log</strong></summary>

```{r analysis-log}
analysis_log <- tibble::tribble(
  ~Category, ~Details,
  "Analysis Start", params$start_time,
  "Analysis End", params$end_time,
  "Input Data and Parameters", "",
  "1. Raster inputs lookup", params$path_lookup_raster_inputs,
  "2. Crop suitability parameters", params$path_lookup_crop_suitability,
  "3. Intervention lookup", params$path_lookup_intervention,
  "Outputs", "",
  "1. Land suitability map (raster)", params$file_name_land_suit_tif,
  "2. Land suitability map lookup table", params$file_name_land_suit_lookup_csv,
  "3. Land suitability map (polygon RDS)", params$file_name_land_suit_rds,
  "4. Soil and climate factors (RDS)", params$file_name_soil_climate_factors_rds,
  "5. Suitability by factors (GeoTIFF)", params$file_name_suit_factors_tif,
  "Output Workspace", params$path_output,
  "Session Summary", ""
) |>
  dplyr::bind_rows(params$session_log)

analysis_log |>
  kbl(caption = "Analysis Log", escape = FALSE) |>
  kable_paper("hover", full_width = FALSE)
```

</details>

---

# Introduction

The primary output of this module is a map that displays areas according to their biophysical suitability for a given crop or farming system. This land suitability map informs users about land suitability and the potential for addressing biophysical limiting factors. However, the map strictly considers biophysical factors and does not account for land allocation maps or maps resulting from specific policies or rules.

In this analysis, it is assumed that according to **Liebig's law of the minimum**, the factor that is at the most limiting level will determine the final suitability level.

<details><summary><strong>Methodology</strong></summary>

### How LaSEM Works

1. **Input Data**: Biophysical raster data (climate, soil, terrain) are classified into suitability classes (S1, S2, S3, N) based on crop-specific thresholds.

2. **Maximum Limitation Method**: For each pixel, the most limiting factor (lowest suitability class) determines the final suitability. This follows Liebig's Law of the Minimum.

3. **Intervention Scenarios**: Potential suitability is calculated by assuming management interventions can improve certain factors by 1-2 classes.

### Key Limitations

- Considers biophysical factors only; socioeconomic factors are excluded.
- The categorical approach does not account for uncertainty in data or interactions between factors.
- Output is semi-quantitative and does not show land productivity in weight per unit area.
- Cannot consider potential impacts of extreme weather events.

</details>

---

# Data Quality

<details><summary><strong>Input Validation Results</strong></summary>

```{r validation-results}
if (!is.null(params$validation_results)) {
  val <- params$validation_results
  if (val$valid) {
    div(class = "alert alert-success", "All input validations passed.")
  } else {
    kable(val$errors, caption = "Validation Errors") |>
      kable_styling(bootstrap_options = c("striped", "hover"))
  }
}
```

</details>

<details><summary><strong>Factor Inspection Log</strong></summary>

```{r inspection-log}
if (!is.null(params$inspection_log) && length(params$inspection_log) > 0) {
  inspection_df <- do.call(rbind, lapply(names(params$inspection_log), function(f) {
    data.frame(
      Factor = f,
      Status = params$inspection_log[[f]]$status,
      Note = ifelse(is.na(params$inspection_log[[f]]$note), "",
                    params$inspection_log[[f]]$note)
    )
  }))
  kable(inspection_df, caption = "Factor Inspection Status") |>
    kable_styling(bootstrap_options = c("striped", "hover"))
}
```

</details>

---

# Crop Environmental Requirements

```{r crop-requirements}
suitability_parameter |>
  select(-c("name_common", "name_sp")) |>
  datatable(options = list(pageLength = 10))
```

---

# Agroclimatic, Soil, and Terrain Conditions

## Input Data Summary

```{r climate-soil-data}
climate_soil_data |>
  select(-c("raster_path")) |>
  datatable(options = list(pageLength = 10))
```

## Input Maps

```{r input-maps, fig.height=10, fig.width=14}
# Create small multiples of input rasters using tidyterra
n_layers <- terra::nlyr(harmonised_rasters)
n_cols <- min(3, n_layers)
n_rows <- ceiling(n_layers / n_cols)

plot_list <- lapply(seq_len(n_layers), function(i) {
  ggplot() +
    tidyterra::geom_spatraster(data = harmonised_rasters[[i]]) +
    scale_fill_viridis_c(name = names(harmonised_rasters)[i]) +
    labs(title = names(harmonised_rasters)[i]) +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 10, face = "bold"),
      axis.text = element_blank(),
      axis.title = element_blank()
    )
})

# Use patchwork to arrange
wrap_plots(plot_list, ncol = n_cols, nrow = n_rows)
```

---

# Crop Suitability Map

## Actual Suitability

```{r suitability-map-static, fig.height=8, fig.width=12}
# Static map using tidyterra with polygon data.
# The GeoTIFF raster does not preserve the active categorical category
# (suitability class) when written and re-read, so we use the polygon
# object which retains the suitability column explicitly.

ggplot() +
  tidyterra::geom_spatvector(data = suitability_polygon, aes(fill = suitability)) +
  scale_fill_manual(
    values = suit_colors,
    labels = suit_labels,
    name = "Suitability",
    na.value = "grey80"
  ) +
  labs(
    title = "Land Suitability Map",
    subtitle = paste(suitability_parameter[["name_common"]][1])
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    legend.position = "right"
  )
```

## Interactive Suitability Map

```{r suitability-map-interactive, fig.height=8, fig.width=12}
# Interactive Leaflet map with layer control for intervention scenarios
if (all(c("suitability_potential_low", "suitability_potential_med", "suitability_potential_high") %in% names(suitability_polygon))) {
  colors_fact <- colorFactor(
    palette = suit_colors,
    levels = c("S1", "S2", "S3", "N"),
    ordered = FALSE
  )

  # Build label content
  suit_poly <- suitability_polygon |>
    sf::st_transform(crs = 4326) |>
    dplyr::mutate(
      label_content = purrr::pmap(
        list(suitability, suitability_potential_high, limiting_factor_actual, limiting_factor_potential),
        function(suit, pot_high, lim_act, lim_pot) {
          lim_act_str <- if (is.null(lim_act) || length(lim_act) == 0 || all(is.na(lim_act))) {
            "None"
          } else {
            paste(unlist(lim_act), collapse = ", ")
          }
          lim_pot_str <- if (is.null(lim_pot) || length(lim_pot) == 0 || all(is.na(lim_pot))) {
            "None"
          } else {
            paste(unlist(lim_pot), collapse = ", ")
          }
          HTML(paste0(
            "<strong>Suitability Actual:</strong> ", suit,
            "<br><strong>Max Potential:</strong> ", pot_high,
            "<br><strong>Primary Limiting Factor:</strong> ", lim_act_str,
            "<br><strong>Secondary Limiting Factor:</strong> ", lim_pot_str
          ))
        }
      )
    )

  leaflet(suit_poly) |>
    addTiles(group = "OSM (default)") |>
    addProviderTiles(leaflet::providers$CyclOSM, group = "CyclOSM") |>
    addPolygons(
      fillColor = ~ colors_fact(suitability),
      fillOpacity = 1,
      color = "grey",
      weight = 0.1,
      smoothFactor = 1,
      label = ~ label_content,
      labelOptions = labelOptions(
        style = list("font-weight" = "normal", "color" = "black"),
        textsize = "13px",
        direction = "auto"
      ),
      group = "Actual"
    ) |>
    addPolygons(
      fillColor = ~ colors_fact(suitability_potential_low),
      fillOpacity = 1,
      color = "grey",
      weight = 0.1,
      smoothFactor = 1,
      label = ~ label_content,
      labelOptions = labelOptions(
        style = list("font-weight" = "normal", "color" = "black"),
        textsize = "13px",
        direction = "auto"
      ),
      group = "Low Intervention"
    ) |>
    addPolygons(
      fillColor = ~ colors_fact(suitability_potential_med),
      fillOpacity = 1,
      color = "grey",
      weight = 0.1,
      smoothFactor = 1,
      label = ~ label_content,
      labelOptions = labelOptions(
        style = list("font-weight" = "normal", "color" = "black"),
        textsize = "13px",
        direction = "auto"
      ),
      group = "Medium Intervention"
    ) |>
    addPolygons(
      fillColor = ~ colors_fact(suitability_potential_high),
      fillOpacity = 1,
      color = "grey",
      weight = 0.1,
      smoothFactor = 1,
      label = ~ label_content,
      labelOptions = labelOptions(
        style = list("font-weight" = "normal", "color" = "black"),
        textsize = "13px",
        direction = "auto"
      ),
      group = "High Intervention"
    ) |>
    addLegend(
      position = "bottomright",
      pal = colors_fact,
      values = ~ factor(c(suitability, suitability_potential_high), levels = c("S1", "S2", "S3", "N")),
      title = "Suitability Level",
      opacity = 0.7
    ) |>
    addLayersControl(
      baseGroups = c("Actual", "Low Intervention", "Medium Intervention", "High Intervention"),
      options = layersControlOptions(collapsed = FALSE)
    )
} else {
  # Fallback message
  p("Interactive map requires potential scenario columns. Please run the full analysis pipeline.")
}
```

## Intervention Scenarios

```{r intervention-maps, fig.height=10, fig.width=14}
# Small multiples for intervention scenarios
pot_cols <- c("suitability_potential_low", "suitability_potential_med",
              "suitability_potential_high")

if (all(pot_cols %in% names(suitability_polygon))) {
  scenario_names <- c("Low Intervention", "Medium Intervention", "High Intervention")

  plot_list <- lapply(seq_along(pot_cols), function(i) {
    col <- pot_cols[i]

    ggplot() +
      tidyterra::geom_spatvector(data = suitability_polygon, aes(fill = !!sym(col))) +
      scale_fill_manual(
        values = suit_colors,
        labels = suit_labels,
        name = "Suitability"
      ) +
      labs(title = scenario_names[i]) +
      theme_minimal() +
      theme(
        plot.title = element_text(size = 12, face = "bold"),
        axis.text = element_blank(),
        axis.title = element_blank()
      )
  })

  wrap_plots(plot_list, ncol = 2, nrow = 2) +
    plot_annotation(
      title = "Suitability Under Different Intervention Scenarios",
      theme = theme(plot.title = element_text(size = 14, face = "bold"))
    )
} else {
  # Fallback message
  ggplot() +
    annotate("text", x = 0.5, y = 0.5,
             label = "Intervention scenario data not available") +
    theme_void()
}
```

---

# Land Suitability by Factor

```{r suitability-factors, fig.height=10, fig.width=14}
# Plot individual factor classifications using a facet grid for consistent legend
raster_df <- as.data.frame(suit_by_factors, xy = TRUE, na.rm = TRUE)

if (ncol(raster_df) > 2) {
  raster_long <- raster_df |>
    tidyr::pivot_longer(
      cols = -c(x, y),
      names_to = "variable",
      values_to = "suitability"
    ) |>
    dplyr::filter(!is.na(suitability)) |>
    dplyr::mutate(
      suitability = factor(suitability, levels = c("S1", "S2", "S3", "N")),
      variable = stringr::str_replace_all(variable, "_", " ")
    )

  ggplot(raster_long, aes(x = x, y = y, fill = suitability)) +
    geom_raster() +
    scale_fill_manual(
      values = suit_colors,
      labels = suit_labels,
      name = "Suitability Class",
      na.value = "grey80"
    ) +
    facet_wrap(~ variable, ncol = min(4, length(unique(raster_long$variable)))) +
    coord_equal() +
    theme_minimal() +
    theme(
      axis.text = element_blank(),
      axis.title = element_blank(),
      strip.text = element_text(size = 10, face = "bold"),
      panel.spacing = unit(2, "mm")
    )
} else {
  ggplot() +
    annotate("text", x = 0.5, y = 0.5,
             label = "No factor classification data available") +
    theme_void()
}
```

---

# Land Suitability Improvements

Assumptions regarding the extent to which actual land suitability can be improved to reach its potential based on the level of management.

```{r intervention-lookup}
intervention_lookup |>
  select(-c("name_parameter")) |>
  datatable(options = list(pageLength = 10))
```

---

# Summary Statistics

```{r area-summary}
if ("suitability" %in% names(suitability_polygon)) {
  # Calculate area in hectares with CRS awareness
  if (sf::st_is_longlat(suitability_polygon)) {
    prev_s2 <- sf::sf_use_s2()
    sf::sf_use_s2(TRUE)
    area_m2 <- as.numeric(sf::st_area(suitability_polygon))
    sf::sf_use_s2(prev_s2)
  } else {
    area_m2 <- as.numeric(sf::st_area(suitability_polygon))
  }

  area_data <- suitability_polygon |>
    sf::st_drop_geometry() |>
    dplyr::mutate(area_ha = round(area_m2 / 10000, 2))

  has_intervention <- all(c(
    "suitability_potential_low", "suitability_potential_med",
    "suitability_potential_high"
  ) %in% names(area_data))

  if (has_intervention) {
    area_stats <- area_data |>
      dplyr::rename(
        Actual = "suitability",
        Low    = "suitability_potential_low",
        Medium = "suitability_potential_med",
        High   = "suitability_potential_high"
      ) |>
      dplyr::select(area_ha, Actual, Low, Medium, High) |>
      tidyr::pivot_longer(
        cols      = c(Actual, Low, Medium, High),
        names_to  = "scenario",
        values_to = "class"
      ) |>
      dplyr::group_by(scenario, class) |>
      dplyr::summarise(area_ha = sum(area_ha, na.rm = TRUE), .groups = "drop") |>
      dplyr::group_by(scenario) |>
      dplyr::mutate(percentage = round(area_ha / sum(area_ha) * 100, 1)) |>
      dplyr::ungroup()

    all_classes <- tidyr::expand_grid(
      scenario = c("Actual", "Low", "Medium", "High"),
      class = c("S1", "S2", "S3", "N")
    )

    area_stats <- all_classes |>
      dplyr::left_join(area_stats, by = c("scenario", "class")) |>
      dplyr::mutate(
        area_ha    = tidyr::replace_na(area_ha, 0),
        percentage = tidyr::replace_na(percentage, 0)
      ) |>
      dplyr::arrange(scenario, match(class, c("S1", "S2", "S3", "N"))) |>
      dplyr::mutate(`Area (ha)` = round(area_ha, 1)) |>
      dplyr::select(Scenario = scenario, Class = class, `Area (ha)`, Percentage = percentage)

    kable(area_stats,
          caption = "Area Distribution by Suitability Class and Intervention Scenario") |>
      kable_styling(bootstrap_options = c("striped", "hover")) |>
      column_spec(1, bold = TRUE) |>
      collapse_rows(columns = 1, valign = "top")
  } else {
    area_stats <- area_data |>
      dplyr::group_by(class = suitability) |>
      dplyr::summarise(area_ha = sum(area_ha, na.rm = TRUE), .groups = "drop") |>
      dplyr::mutate(percentage = round(area_ha / sum(area_ha) * 100, 1)) |>
      dplyr::mutate(`Area (ha)` = round(area_ha, 1)) |>
      dplyr::select(Class = class, `Area (ha)`, Percentage = percentage) |>
      dplyr::arrange(match(Class, c("S1", "S2", "S3", "N")))

    kable(area_stats,
          col.names = c("Suitability Class", "Area (ha)", "Percentage (%)"),
          caption = "Area Distribution by Suitability Class") |>
      kable_styling(bootstrap_options = c("striped", "hover"))
  }
}
```

---

<details><summary><strong>Session Information</strong></summary>

```{r session-info}
kable(params$session_log, caption = "R Session Information") |>
  kable_styling(bootstrap_options = c("striped", "hover"))
```

</details>

---

<font size="1">LUMENS is free software and comes with ABSOLUTELY NO WARRANTY. Users are responsible for the results generated. Results depend on the quality of the input data ("garbage in, garbage out") and may vary or be sensitive to the parameters used. Please report any problems encountered while using LUMENS as [a GitHub issue](https://github.com/icraf-indonesia/lumens-shiny/issues).</font>
