---
title: "SCIENDO-Simulate Report"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: united
    highlight: tango
    df_print: kable
params:
  start_time: NA
  end_time: NA
  inputs: NA
  session_log: NA  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load function, include=FALSE, error=TRUE, warning=TRUE, message=TRUE}
source("../rscript/function_sciendo_simulate.R")
```

```{r load_library, include=FALSE}
library(raster)
library(dplyr)
library(DT)
library(kableExtra)
library(htmltools)
library(LUMENSR)
```

<details><summary>Click here for Analysis Log</summary>

```{r analysis-log, echo=FALSE}
analysis_log <- tribble(
  ~Category,                       ~Details,
  "Analysis Start",                params$start_time,
  "Analysis End",                  params$end_time,
  "Input Data and Parameters",     "",
  "1. Landcover map initial",      params$inputs$lc_t1_path,
  "2. Planning unit",              params$inputs$zone_path,
  "3. Land cover lookup table",    params$inputs$lc_lookup_table_path,
  "4. Raster cube",                params$inputs$ers_path,
  "5. Transition matrix directory",params$inputs$tm_path,
  "6. WoE directory",              params$inputs$dcf_path,
  "Output Workspace",              params$inputs$output_dir,
  "Session Summary",               ""
) %>% rbind(params$session_log)

analysis_log %>% kbl(caption = "Analysis Log", escape = FALSE) %>%
  kable_paper("hover", full_width = F )
```

</details>

# Summary

```{r input-data, echo=FALSE, message=FALSE, warning=FALSE}

```

This report presents the results of an analysis based on the provided maps and lookup table.


# Module brief description

- SCIENDO-Simulate


# Input data {.tabset}

## Land-Use/Cover Map Initial

```{r Land-Use/Cover Map T1, echo=FALSE, message=FALSE, warning=FALSE}

```


## Planning Unit

```{r Planning Unit, echo=FALSE, message=FALSE, warning=FALSE}

```


# Results

## Land Use Change Projection


------------------------------------------------------------------------

<!-- Mandatory closing statement for all module -->

<font size="1"> LUMENS is free software and comes with ABSOLUTELY NO WARRANTY. Users are responsible for the results generated. Results depend on the quality of the input data ("garbage in, garbage out") and may vary or be sensitive to the parameters used. Please report any problems encountered while using LUMENS as [a GitHub issue](https://github.com/icraf-indonesia/lumens-shiny/issues). Feedback and questions are welcome [Contact Us URL]. </font size>