---
title: "Trade-off Analysis Regional 2 Report"
author: "System"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    theme: united
    highlight: tango
    df_print: paged
params:
  LC_graph: NA
  GDP_graph: NA
  LAB_graph: NA
  landuse_table: NA
  GDP_summary: NA
  Labour_table: NA
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(raster)
```

## Introduction

This report presents the results of an analysis based on the provided maps and lookup table

## Lookup Table Summary

* A brief description or summary statistics of the lookup table data can be included here.

## Analysis Results

The maps provided was carbon, emission and sequestration map.

* Calculation or analysis details based on the results can be presented here.

### Direct Backward Linkages graph

```{r}
head(params$landuse_table, n=20)
plot(params$LC_graph)
```

### Direct Forward Linkages graph 

```{r}
head(params$GDP_summary, n=20)
plot(params$GDP_graph)
```

### Land Requirement Coefficient graph 

```{r}
head(params$Labour_table, n=20)
plot(params$LAB_graph)
```

## Conclusion

* Summarize the key findings or insights from the analysis.
