---
title: "Trade-off Analysis Regional 2 Report"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: kable
params:
  LAB_graph: NA
  landuse_table: NA
  Labour_table: NA
  GDP_totals_graph : NA
  GDP_scen_df: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(ggplot2)
library(raster)
```

## Introduction

This report presents the results of an analysis based on the provided maps and lookup table

## Lookup Table Summary

* A brief description or summary statistics of the lookup table data can be included here.

## Analysis Results

The maps provided was carbon, emission and sequestration map.

* Calculation or analysis details based on the results can be presented here.

### GDP Each Sector

```{r, echo=FALSE, warning=FALSE, message=FALSE}
knitr::kable(params$GDP_scen_df)
```

### GDP Total
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(params$GDP_totals_graph)
```
## Conclusion

* Summarize the key findings or insights from the analysis.
