---
title: "QuES-C Report"
author: "System"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    theme: united
    highlight: tango
    df_print: paged
params:
  map_c1: NA
  map_c2: NA
  map_em: NA
  map_sq: NA
  ques_db: NA
  p1: NA
  p2: NA
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(raster)
```

## Introduction

This report presents the results of an analysis based on the provided maps and lookup table

## Lookup Table Summary

The uploaded lookup table contains `r nrow(params$ques_db)` rows and `r names(params$ques_db)` columns.

* A brief description or summary statistics of the lookup table data can be included here.

```{r}
head(params$ques_db, n=20)
```


## Analysis Results

The maps provided was carbon, emission and sequestration map.

* Calculation or analysis details based on the results can be presented here.

### Carbon map `r nrow(params$p1)`

```{r}
plot(params$map_c1)
```

### Carbon map `r nrow(params$p2)`

```{r}
plot(params$map_c2)
```

### Emission map 

```{r}
plot(params$map_em)
```

### Sequestration map 

```{r}
plot(params$map_sq)
```

## Conclusion

* Summarize the key findings or insights from the analysis.
