---
title: "Trade-off Analysis Regional 1 Report"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: kable
params:
  BPD_graph: NA
  FPD_graph: NA
  LRC_graph: NA
  Linkages_table: NA
  land.requirement_table: NA
  PRS_graph : NA 
  GDP : NA 
  GDP_graph : NA 
  multiplier : NA
  OMPL_graph : NA 
  IMPL_graph : NA 
  LMPL_graph : NA 
  P.sector.selected : NA
---

```{r setup, include = FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(ggplot2)
library(raster)
```

## Introduction

This report presents the results of an analysis based on the provided maps and lookup table

## Lookup Table Summary

* A brief description or summary statistics of the lookup table data can be included here.

## Analysis Results

The maps provided was carbon, emission and sequestration map.

* Calculation or analysis details based on the results can be presented here.

## Analysis of Sectoral Linkages 
### Table 1. Sectoral linkages

```{r, echo=FALSE, warning=FALSE, message=FALSE}
knitr::kable(params$Linkages_table)
```

### Direct Backward Linkages graph
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(params$BPD_graph)
```

### Direct Forward Linkages graph 
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(params$FPD_graph)
```

### Sectoral typology based on linkages analysis
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(params$PRS_graph)
```

### Primary sectors based on potential linkage
```{r, echo=FALSE, warning=FALSE, message=FALSE}
knitr::kable(params$P.sector.selected)
```

## Analysis of GDP 
### Sectoral GDP Table
```{r, echo=FALSE, warning=FALSE, message=FALSE}
knitr::kable(params$GDP)
```

### GDP graph 
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(params$GDP_graph)
```

## Analysis of multiplier 
### Sectoral Multiplier
```{r, echo=FALSE, warning=FALSE, message=FALSE}
knitr::kable(params$multiplier)
```

### Output Multiplier
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(params$OMPL_graph)
```

### Input Multiplier
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(params$IMPL_graph)
```

### Labour Multiplier
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(params$LMPL_graph)
```

### Land Requirement Table
```{r, echo=FALSE, warning=FALSE, message=FALSE}
knitr::kable(params$land.requirement_table)
```

### Land Requirement Coefficient Graph 
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(params$LRC_graph)
```

## Conclusion

* Summarize the key findings or insights from the analysis.
