---
title: "Trade-off Analysis Profit Report"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: kable
params:
  map_carbon1: NA
  map_carbon2: NA
  emission_map: NA
  opcost_map: NA
  opcost_table: NA
  opcost_curve: NA
  npv1_map: NA
  npv2_map: NA
  delta_npv: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(raster)
```

## Introduction

This report presents the results of an analysis based on the provided maps and lookup table

## Lookup Table Summary


* A brief description or summary statistics of the lookup table data can be included here.


## Analysis Results

The maps provided was carbon, emission and sequestration map.

* Calculation or analysis details based on the results can be presented here.

### Opportunity Cost Table

```{r, echo=FALSE, warning=FALSE, message=FALSE}
head(params$opcost_table, n=10)
```

### Opportunity Cost Curve
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(params$opcost_curve)
```

### NPV Map 1

```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(params$npv1_map)
```

### NPV Map 2
```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(params$npv2_map)
```

### Delta NPV Map

```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot(params$delta_npv)
```

## Conclusion

* Summarize the key findings or insights from the analysis.
