---
title: "Profitability Analysis Report"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: kable
params:
  session_log: NA
  start_time: NA
  end_time: NA
  total_table : NA
  npv1_table : NA
  npv2_table : NA
  deltaNPV_table : NA
  npv1_chart : NA
  npv2_chart : NA
  deltaNPV_chart : NA
  npv1_map: NA
  npv2_map: NA
  deltaNPV_map: NA
  map1_file_path: NULL
  map2_file_path: NULL
  npv_file_path: NULL
  carbon_file_path: NULL
  pu_table_path: NULL
  year1: NULL
  year2: NULL
  output_dir: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(kableExtra)
library(tidyr)
library(pkgdown)
library(ggplot2)
library(htmlwidgets)
library(DT)
```


<details><summary>Click here for Analysis Log</summary>

```{r analysis-log, echo=FALSE}

analysis_log <- tribble(
  ~Category,                   ~Details,
  "Analysis Start",        params$start_time,
  "Analysis End",          params$end_time,
  "Input Data and Parameters", "",
  "Land Cover (t1)",      params$map1_file_path,
  "Land Cover (t2)",   params$map2_file_path,
  "Profitability data",   params$npv_file_path,
  "Carbon stock data",   params$carbon_file_path,
  "Year 1", as.character(params$year1),
  "Year 2", as.character(params$year2),
  "NoData land-cover class", as.character(params$raster_nodata),
  "Output Files", "",
  "Output Workspace",      paste0(getwd(), " | ", params$output_dir),
  "Session Summary", "",
) %>% rbind(format_session_info_table())

analysis_log %>% kbl(caption = "Analysis Log", escape = FALSE) %>%
  kable_paper("hover", full_width = F )
```
</details>

# Introduction

This report presents the results of a Profitability Analysis based on land-use change scenarios. The analysis focuses on assessing the net present value (NPV) associated with different land-use changes. This approach helps evaluate the financial and environmental implications of land use transitions and supports informed decision-making that balances economic viability with sustainability goals.

# Analysis Results

The analysis workflow involves several key steps:

1. **NPV and Carbon Data Processing**: NPV and carbon data were combined to create a comprehensive lookup table.
2. **Land-Use Change Analysis**: The land-use change maps were processed to assess changes in NPV.
3. **Visualization**: Maps were generated to visually represent the spatial distribution of NPV changes. 

## Summary of Net Present Value (NPV)
```{r, echo=FALSE, warning=FALSE, message=FALSE}
params$total_table %>%
  as.data.frame() %>%
  dplyr::mutate(dplyr::across(where(is.numeric), scales::label_comma())) %>%
  DT::datatable()
```

### NPV for `r params$year1` {.tabset}
This section presents the ten land cover categories with the highest total Net Present Value (NPV) in `r params$year1`, which represents the cumulative economic return (in Rupiah or USD) derived from land use activities over a given area, typically measured in hectares. NPV is a key metric in land use planning as it reflects the present value of future benefits associated with different land uses in `r params$year1`.

#### Plot
```{r, echo=FALSE, warning=FALSE, message=FALSE}
params$npv1_chart
```

#### Table
```{r, echo=FALSE, warning=FALSE, message=FALSE}
params$npv1_table %>%
  dplyr::mutate(dplyr::across(where(is.numeric), easy_to_read_numbers)) %>%
  rename(
    `Land Cover 1` = LC1,
    `Total NPV (Rupiah)` = Total_NPV1,
    `Total Area (Ha)` = Total_Ha1
  ) %>%
  DT::datatable(rownames = FALSE)
```

### NPV for `r params$year2` {.tabset}
This section presents the ten land cover categories with the highest total Net Present Value (NPV) in `r params$year2`, which represents the cumulative economic return (in Rupiah or USD) derived from land use activities over a given area, typically measured in hectares. NPV is a key metric in land use planning as it reflects the present value of future benefits associated with different land uses in `r params$year2`.

#### Plot
```{r, echo=FALSE, warning=FALSE, message=FALSE}
params$npv2_chart
```

#### Table
```{r, echo=FALSE, warning=FALSE, message=FALSE}
params$npv2_table %>%
  dplyr::mutate(dplyr::across(where(is.numeric), easy_to_read_numbers)) %>%
  rename(
    `Land Cover 2` = LC2,
    `Total NPV (Rupiah)` = Total_NPV2,
    `Total Area (Ha)` = Total_Ha2
  ) %>%
  DT::datatable(rownames = FALSE)
```


### Delta NPV for `r params$year1` to `r params$year2` {.tabset}
This section presents the change in Net Present Value (ΔNPV) between the years `r params$year1` and `r params$year2`. ΔNPV reflects the difference in projected economic returns from land use across the two time periods. Positive ΔNPV values indicate an increase in profitability over time, while negative values suggest a decline. 

#### Plot
```{r, echo=FALSE, warning=FALSE, message=FALSE}
params$deltaNPV_chart
```

#### Table
```{r, echo=FALSE, warning=FALSE, message=FALSE}
params$deltaNPV_table %>%
  dplyr::mutate(dplyr::across(where(is.numeric), easy_to_read_numbers)) %>%
  rename(
    `Land Use Change` = LULCC,
    `ΔNPV (Rupiah)` = Total_deltaNPV,
    `|ΔNPV| (Rupiah)` = Total_abs_deltaNPV,
    `Total Area (Ha)` = Total_Ha2
  ) %>%
  DT::datatable(rownames = FALSE)
```

## Net Present Value (NPV) Distribution Maps
The NPV Maps are critical visual outputs that illustrate the financial performance of different land-use categories at two distinct points in time. These maps help in understanding how land-use changes over time impact profitability, providing valuable insights for decision-makers seeking to balance economic and environmental factors.

### NPV Map for Year `r params$year1`
This map serves as a baseline for understanding the initial profitability of different land uses before any land-use changes occur. The map visually displays areas with varying degrees of profitability, using color gradients to indicate the range of NPV values.
```{r, echo=FALSE, warning=FALSE, message=FALSE}
npv1_map <- ggplot() +
  tidyterra::geom_spatraster(data = params$npv1_map) +
  scale_fill_gradient(
    low = "yellow",
    high = "darkgreen",
    na.value = "white",
    name = "NPV"
  ) +
  theme_bw() +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8),
    legend.key.height = unit(1, "cm"),
    legend.key.width = unit(0.25, "cm"),
    legend.position = "right",
    legend.justification = c(0, 0.5)
  )

npv1_map
```

### NPV Map for Year `r params$year2`
This map captures how the financial value of different land uses has evolved over the analysis period due to land-use changes, policy interventions, or natural factors. Like NPV Map for Year `r params$year1`, it uses color gradients to indicate the profitability of various land areas.
```{r, echo=FALSE, warning=FALSE, message=FALSE}
npv2_map <- ggplot() +
  tidyterra::geom_spatraster(data = params$npv2_map) +
  scale_fill_gradient(
    low = "yellow",
    high = "darkgreen",
    na.value = "white",
    name = "NPV"
  ) +
  theme_bw() +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8),
    legend.key.height = unit(1, "cm"),
    legend.key.width = unit(0.25, "cm"),
    legend.position = "right",
    legend.justification = c(0, 0.5)
  )

npv2_map
```

### Delta NPV Map
This map highlights the regions where significant changes in NPV occurred due to land-use changes. Areas with high profitability shifts are marked in green, while those with reduced profitability are marked in red.
```{r, echo=FALSE, warning=FALSE, message=FALSE}
deltaNPV_map <- ggplot() +
  tidyterra::geom_spatraster(data = params$deltaNPV_map) +
  scale_fill_gradient(
    low = "red",
    high = "darkgreen",
    na.value = "white",
    name = "NPV"
  ) +
  theme_bw() +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8),
    legend.key.height = unit(1, "cm"),
    legend.key.width = unit(0.25, "cm"),
    legend.position = "right",
    legend.justification = c(0, 0.5)
  )

deltaNPV_map
```


## NPV Results at the Planning Unit Level

```{r child_documen_traj_fao, echo=FALSE, fig.keep='all', results='asis'}
render_child_pu <- function(results_list, pu_name) {
  res <- knitr::knit_child(
    text = c(
      paste0("### ", pu_name, " {.tabset}"),
      "",
      paste0("#### Total Value Table for ", pu_name),
      "```{r}",
      "#| echo: false",
      "as.data.frame(results_list[[pu_name]][['total_values']]) %>%",
      "  mutate_if(is.numeric, easy_to_read_numbers) %>%",
      "  kable() %>%",
      "  kable_styling(bootstrap_options = c('striped', 'hover'))",
      "```",
      "",
      paste0("#### Top 10 NPV by LC 1 in ", pu_name),
      "```{r}",
      "#| echo: false",
      "results_list[[pu_name]][['lc1_bar']]",
      "```",
      "",
      paste0("#### Top 10 NPV by LC 2 in ", pu_name),
      "```{r}",
      "#| echo: false",
      "results_list[[pu_name]][['lc2_bar']]",
      "```",
      "",
      paste0("#### Top 10 ΔNPV in ", pu_name),
      "```{r}",
      "#| echo: false",
      "results_list[[pu_name]][['lulcc_bar']]",
      "```"
    ),
    envir = rlang::env(results_list = results_list, pu_name = pu_name),
    quiet = TRUE
  )
  cat(res, sep = "\n")
  cat("\n")
}

for (pu_name in names(pu_outputs)) {
  render_child_pu(pu_outputs, pu_name)
}
```

# Conclusion
The report highlights the key trade-offs between financial returns and environmental sustainability. It provides insights for decision-makers to balance profitability with environmental responsibility in land-use planning. The generated maps and opportunity cost curves serve as tools for evaluating these trade-offs across various scenarios.


------------------------------------------------------------------------


<font size="1"> LUMENS is free software and comes with ABSOLUTELY NO WARRANTY. Users are responsible for the results generated. Results depend on the quality of the input data ("garbage in, garbage out") and may vary or be sensitive to the parameters used. Please report any problems encountered while using LUMENS as [a GitHub issue](https://github.com/icraf-indonesia/lumens-shiny/issues). Feedback and questions are welcome [Contact Us URL]. </font size>
